---
title: "Untitled"
output: html_document
---

# --- Settings ---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# --- Packages ---

```{r}
library(readxl)
library(tidyverse)
library(lubridate)
library(binom)

library(zoo)

```

# --- Load Data ---

## 1. load csv

```{r}
if (FALSE){
t1 <- Sys.time()
cov_raw <- read.csv("COVID-19_Case_Surveillance_Public_Use_Data.csv")
Sys.time() - t1
}
```
## 2. save as Rda

```{r}
if (FALSE){
save(cov_raw,
     file = "cov_raw.Rda")
}
```


## 3. load RDa

```{r}
if (TRUE){
  t1 <- Sys.time()
  load("cov_raw.Rda")
  Sys.time() - t1
}
```

## 2. view

```{r}
View(cov_raw)
```

## 3. types

```{r}
# examine cols&types
t(data.frame(lapply(cov_raw, class)))
```

# --- Analysis ---

## 1. check how many possible diagnoses there are

```{r}
unique(cov_raw$current_status)
```

## 2. check what counts as positive case

```{r}
cov <-
cov_raw %>% 
 rename_at(1, ~"date_earliest") %>% 
 rename(date_report = cdc_report_dt,
        date_spec = pos_spec_dt) %>% 
  mutate(date_earliest = as.Date(date_earliest),
         date_report = as.Date(date_report),
         date_spec = as.Date(date_spec))
cov
```


select a few dates, and compare case counts from gov website on each date, to case counts, using the 3 possible date vars

-- gov tracker: https://covid.cdc.gov/covid-data-tracker/#trends_dailytrendscases
-- few dates:
--> sep 19, 2020: 42,580
--> sep 20, 2020: 37,459
--> nov 14, 2020: 197,622
--> nov 15, 2020: 101,847
--> jan 2, 2021: 285,002
--> jan 3, 2021: 212,496 

```{r}
cov %>% 
  filter(date_earliest == "2020-09-19" | date_report == "2020-09-19" | date_spec == "2020-09-19") %>% 
  pivot_longer(cols = c(date_earliest, date_report, date_spec),
               names_to = "date_type",
               values_to = "date") %>% 
  select(date_type, date, everything()) %>% 
  group_by(date_type, date, current_status) %>% 
  filter(date == "2020-09-19") %>% 
  count() %>% 
  arrange(desc(date), desc(n))

```

```{r}
cov %>% 
  filter(date_earliest == "2020-10-15" | date_report == "2020-10-15" | date_spec == "2020-10-15") %>% 
  pivot_longer(cols = c(date_earliest, date_report, date_spec),
               names_to = "date_type",
               values_to = "date") %>% 
  select(date_type, date, everything()) %>% 
  group_by(date_type, date, current_status) %>%
  filter(date == "2020-10-15") %>%
  count() %>% 
  arrange(desc(date), desc(n))

```

```{r}
cov %>% 
  filter(date_earliest == "2021-01-03" | date_report == "2021-01-03" | date_spec == "2021-01-03") %>% 
  pivot_longer(cols = c(date_earliest, date_report, date_spec),
               names_to = "date_type",
               values_to = "date") %>% 
  select(date_type, date, everything()) %>% 
  group_by(date_type, date, current_status) %>%
  filter(date == "2021-01-03") %>%
  count() %>% 
  arrange(desc(date), desc(n))

```

## 3. shape date

-- count towards daily case count:
-- date_earliest  + date_report (laboratory confirmed case)

```{r}
cov_sum <-
cov %>% 
  filter(current_status == "Laboratory-confirmed case" ) %>% 
  # filter(date_earliest >= "2021-01-15" | date_report >= "2021-01-15") %>% 
  pivot_longer(cols = c(date_earliest, date_report, date_spec),
               names_to = "date_type",
               values_to = "date") %>% 
  filter(date_type == "date_earliest" | date_type == "date_report") %>% 
  select(date_type, date, everything()) %>% 
  group_by(date_type, date, current_status) %>%
  count() %>% 
  arrange(date, desc(n))
cov_sum

```

merge together dates

```{r}
cov_approx <-
cov_sum %>% 
  group_by(date) %>%
  mutate(approx_total = sum(n)) %>% 
  filter(date_type == "date_earliest") %>%  # doesn't matter either way
  select(date, approx_total)
cov_approx

```


## 4. save shaped data

```{r}
save(cov_approx, file = "cov_approx.Rda")
```

## 5. graph

```{r, fig.width=8, fig.height=5}
cov_approx %>% 
  ggplot(aes(x = date,
             y = approx_total)) +
  geom_point() +
  geom_line()

```

# 6. enter 7 day moving average projections

```{r}
cov_7d <- tibble::tribble(~date, ~num_days, ~avg,
                          "2021-01-12", 1, 246895,
                          "2021-01-17", 6, 216701,
                          "2021-01-21", 10, 188416,
                          "2021-01-23", 12, 174620,
                          "2021-01-26", 15, 166496,
                          "2021-01-30", 19, 149348,
                          "2021-02-01", 21, 143968,
                          "2021-02-03", 23, 134523,
                          "2021-02-05", 25, 124773)
cov_7d
```

# 7. get difference in time length between days

```{r}
# tests/checks
time_length(x = interval(ymd("2021-01-12"), ymd("2021-01-13")), unit = "days")
time_length(x = interval(ymd("2021-01-12"), ymd("2021-01-14")), unit = "days")
time_length(x = interval(ymd("2021-01-12"), ymd("2021-01-15")), unit = "days")
time_length(x = interval(ymd("2021-01-12"), ymd("2021-01-31")), unit = "days")
time_length(x = interval(ymd("2021-01-12"), ymd("2021-02-01")), unit = "days")
time_length(x = interval(ymd("2021-01-12"), ymd("2021-02-02")), unit = "days")
time_length(x = interval(ymd("2021-01-12"), ymd("2021-02-15")), unit = "days")

# main question
print("--------")
time_length(x = interval(ymd("2021-01-12"), ymd("2021-03-15")), unit = "days")
```


# 8. graph: moving average

```{r, fig.width=10, fig.height=7}
cov_7d %>% 
  ggplot(aes(x = num_days,
             y = avg)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 62) +
  scale_y_continuous(breaks = seq(-100e3, 250e3, 10e3),
                     limits = c(-100e3, 250e3)) +
  scale_x_continuous(breaks = seq(1, 70, 5),
                     limits = c(1,70)) +
  geom_smooth(method = "lm", fullrange = TRUE) +
  theme_bw()

```


# 9. month window looking back (lowest)

```{r}
cov_approx$stat_min30 <- zoo::rollapply(data = cov_approx$approx_total, FUN = min, width = 30)
temp <- zoo::rollapply(data = cov_approx$approx_total, FUN = min, width = 30)
temp

d <- data.frame(cbind(1:length(temp), temp))
colnames(d) <- c("day_num", "min_30")
d
```

```{r, fig.height=8, fig.width=10}
d %>% 
ggplot(aes(x = day_num,
           y = min_30)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 50e3,
             color = "red",
             linetype = "dotted") +
  scale_y_continuous(breaks = seq(-100e3, 250e3, 10e3)) +
  scale_x_continuous(breaks = seq(1, 1000, 10)) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))
```



# --- MISC/END ---

```{r}
z <- zoo(11:15, as.Date(31:35))
z
rollapply(data = z, FUN = min, width = 2)
```








