---
title: "elon_tweets"
output: html_document
---

# Settings

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r}
library(tidyverse)
library(lubridate)
library(readxl)
```

# Load Data

Downloaded tweets from here: https://www.vicinitas.io/free-tools/download-user-tweets

```{r}
elon_raw <- read_excel("@elonmusk_user_tweets.xlsx")
```

# View Data

```{r}
View(elon_raw)
```


# Shape Data

See documentation on how exactly a week is calculated

```{r}
elon <-
elon_raw %>% 
  select(UTC, `Tweet Id`, Text) %>%
  rename("tweet_id" = `Tweet Id`) %>%
  mutate(date = ymd_hms(UTC)) %>% 
  arrange(date) %>% 
  mutate(year = year(date),
         month = month(date, label = TRUE),
         week = week(date),
         day = wday(date, label = TRUE)) %>% 
  select(date, year, month, week, day, everything()) %>% 
  filter(!(week == 4 & year == 2021), # filter out unfinished weeks (this week, last week of 2020, first week in data set)
         !(week == 12 & year == 2020),
         !(week == 53 & year == 2020)) # filter out unfinished weeks
  
elon
```


# Tweets Per Week

```{r}
weekly_tweets <-
elon %>% 
  group_by(year, week) %>% 
  count(year, week)

weekly_tweets

```

# Check Time frame

```{r}
min(elon$date)
max(elon$date)
```
# Weekly Tweets, Quantiles

```{r}
quantile(x = weekly_tweets$n,
         probs = c(0.01, 0.025, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.975, 0.99))
```
# Weekly Tweets, "Reverse Quantiles" (based on Polymarket cuts)

method from here: https://stat.ethz.ch/pipermail/r-help/2012-March/305368.html

```{r}
ecdf(weekly_tweets$n)(c(49, 50, 59, 60, 69, 70, 79, 80))
```
get probability of falling in various ranges

```{r}
# historical averages
print("HISTORICAL AVERAGES")
# 49 or less
print(paste0("49 or less: ", round(ecdf(weekly_tweets$n)(49), 2)))

# 50 to 59
print(paste0("50 to 59: ", round(ecdf(weekly_tweets$n)(59) - ecdf(weekly_tweets$n)(50), 2)))

# 60 to 69
print(paste0("60 to 69: ", round(ecdf(weekly_tweets$n)(69) - ecdf(weekly_tweets$n)(60), 2)))

# 70 to 79
print(paste0("70 to 79: ", round(ecdf(weekly_tweets$n)(79) - ecdf(weekly_tweets$n)(70), 2)))

# 80 or more
print(paste0("80 or more: ", round(1 - ecdf(weekly_tweets$n)(80), 2)))
print("-----------------")

# current prices
print("CURRENT PRICES")
print("49 or less: $0.25")
print("50 to 59: $0.25")
print("60 to 69: $0.21")
print("70 to 79: $0.14")
print("80 or more: $0.15")

```

inspect ecdf

```{r}
ecdf(weekly_tweets$n)
```


# Weekly Tweets, Graph (basic)

```{r, fig.height=6, fig.width=12}
weekly_tweets %>% 
  ggplot(aes(x = week,
             y = n,
             color = as.factor(year))) +
  geom_point(size = 2) +
  geom_line(size = 1.25,
            alpha = 0.5) +
  theme_bw() +
  labs(title = "Tweets per Week (@elonmusk)",
       x = "Week of the Year",
       y = "Number of Tweets",
       color = "Year") +
  scale_x_continuous(breaks = seq(0, 52, 1)) +
  scale_y_continuous(breaks = seq(0, 160, 5)) +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank())

```

# Weekly Tweets, Graph (percentile overlay)


```{r, fig.height=6, fig.width=12}

weekly_tweets %>% 
  ggplot(aes(x = week,
             y = n,
             color = as.factor(year))) +
  geom_point(size = 2) +
  geom_line(size = 1.25,
            alpha = 0.5) +
  theme_bw() +
  labs(title = "Tweets per Week (@elonmusk)",
       x = "Week of the Year",
       y = "Number of Tweets",
       color = "Year") +
  scale_x_continuous(breaks = seq(0, 52, 1)) +
  scale_y_continuous(breaks = seq(0, 160, 5)) +
  geom_hline(yintercept = quantile(weekly_tweets$n, probs = c(0.01, 0.10, 0.25, 0.50, 0.75, 0.90, 0.99)),
             linetype = c("dotted", "dotted", "dotted", "solid", "dotted", "dotted", "dotted")) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.01) + 3, x = 8, label = "1st percentile", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.10) + 3, x = 8, label = "10th percentile", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.25) + 3, x = 8, label = "25th percentile", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.50) + 3, x = 8, label = "50th percentile (median)", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.75) + 3, x = 8, label = "75th percentile", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.90) + 3, x = 8, label = "90th percentile", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.99) + 3, x = 8, label = "99th percentile", size = 3.5) +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())


```

# histogram (basic)

```{r, fig.height=6, fig.width=12}
weekly_tweets %>% 
  ggplot(aes(x = n)) +
  geom_density() +
  scale_x_continuous(breaks = seq(0, 160, 5)) +
  scale_y_continuous(breaks = seq(0, 1, 0.001)) +
  labs(title = "Distribution of Tweeks per Week (@elonmusk)",
       x = "Weekly Tweet Count",
       y = "Proportion of Observations") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

```

# histogram (percentile overlay)

```{r, fig.height=6, fig.width=12}
weekly_tweets %>% 
  ggplot(aes(x = n)) +
  geom_density(size = 2) +
  scale_x_continuous(breaks = seq(0, 160, 5)) +
  scale_y_continuous(breaks = seq(0, 1, 0.001)) +
  labs(title = "Distribution of Tweeks per Week (@elonmusk)",
       x = "Weekly Tweet Count",
       y = "Proportion of Observations") +
  geom_vline(xintercept = quantile(weekly_tweets$n, probs = c(0.01, 0.10, 0.25, 0.50, 0.75, 0.90, 0.99)),
             linetype = c("dotted", "dotted", "dotted", "solid", "dotted", "dotted", "dotted")) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.01) + 1, y = 0.004, label = "1st percentile", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.10) + 1, y = 0.004, label = "10th percentile)", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.25) + 1, y = 0.004, label = "25th percentile", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.50) + 1, y = 0.004, label = "50th percentile (median)", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.75) + 1, y = 0.004, label = "75th percentile", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.90) + 1, y = 0.004, label = "90th percentile", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.99) + 1, y = 0.004, label = "99th percentile", size = 3.5, angle = 90) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

```


# MISC/END

