---
title: "elon_tweets"
output: html_document
---

# Settings

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r}
library(tidyverse)
library(lubridate)
library(readxl)
```

# Load Data

Downloaded tweets from here: https://www.vicinitas.io/free-tools/download-user-tweets

```{r}
tweets_raw <- read_excel("@MCuban_user_tweets.xlsx")
```

# View Data

```{r}
View(tweets_raw)
```


# Shape Data

See documentation on how exactly a week is calculated

```{r}
tweets<-
tweets_raw %>% 
  select(UTC, `Tweet Id`, Text) %>%
  rename("tweet_id" = `Tweet Id`) %>%
  mutate(date = ymd_hms(UTC)) %>% 
  arrange(date) %>% 
  mutate(year = year(date),
         month = month(date, label = TRUE),
         week = week(date),
         day = wday(date, label = TRUE)) %>% 
  select(date, year, month, week, day, everything()) %>% 
  filter(!(week == 4 & year == 2021), # filter out unfinished weeks (this week, last week of 2020, first week in data set)
         !(week == 12 & year == 2020),
         !(week == 53 & year == 2020)) # filter out unfinished weeks
  
tweets
```


# Tweets Per Week

```{r}
weekly_tweets <-
tweets %>% 
  group_by(year, week) %>% 
  count(year, week)

weekly_tweets

```

# Check Time frame

```{r}
min(tweets$date)
max(tweets$date)
```
# Weekly Tweets, Quantiles

```{r}
quantile(x = weekly_tweets$n,
         probs = c(0.01, 0.025, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.975, 0.99))
```
# Weekly Tweets, Quantiles (2020)

```{r}
quantile(x = weekly_tweets[weekly_tweets$year==2020,]$n,
         probs = c(0.01, 0.025, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.975, 0.99),
         na.rm = TRUE)
```

# Weekly Tweets, Quantiles (2021)

```{r}
quantile(x = weekly_tweets[weekly_tweets$year==2021,]$n,
         probs = c(0.01, 0.025, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.975, 0.99),
         na.rm = TRUE)
```

# Weekly Tweets, "Reverse Quantiles" (based on Polymarket cuts)

method from here: https://stat.ethz.ch/pipermail/r-help/2012-March/305368.html

```{r}
ecdf(weekly_tweets$n)(c(49, 50, 59, 60, 69, 70, 79, 80))
```
# Weekly Tweets, "Reverse Quantiles" just 2020 (based on Polymarket cuts)

method from here: https://stat.ethz.ch/pipermail/r-help/2012-March/305368.html

```{r}
ecdf(weekly_tweets[weekly_tweets$year==2020,]$n)(c(30, 30, 39, 40, 49, 50, 59, 60, 69, 70))
```


get probability of falling in various ranges

```{r}
# historical averages
print("HISTORICAL AVERAGES")
# 49 or less
print(paste0("29 or less: ", round(ecdf(weekly_tweets$n)(29), 2)))

# 50 to 59
print(paste0("30 to 39: ", round(ecdf(weekly_tweets$n)(39) - ecdf(weekly_tweets$n)(30), 2)))

# 60 to 69
print(paste0("40 to 49: ", round(ecdf(weekly_tweets$n)(49) - ecdf(weekly_tweets$n)(40), 2)))

# 70 to 79
print(paste0("50 to 59: ", round(ecdf(weekly_tweets$n)(59) - ecdf(weekly_tweets$n)(50), 2)))

# 70 to 79
print(paste0("60 to 69: ", round(ecdf(weekly_tweets$n)(69) - ecdf(weekly_tweets$n)(60), 2)))

# 80 or more
print(paste0("70 or more: ", round(1 - ecdf(weekly_tweets$n)(70), 2)))
print("-----------------")

# current prices
print("CURRENT PRICES (feb 2, 12:21 am")
print("29 or less: $0.19")
print("30 to 39: $0.24")
print("40 to 49: $0.18")
print("50 to 59: $0.14")
print("60 to 69: $0.11")
print("80 or more: $0.14")

```

get probability of falling in various ranges (JUST 2020)

```{r}
weekly_tweets_2020 <- weekly_tweets[weekly_tweets$year==2020,]

# historical averages
print("HISTORICAL AVERAGES, JUST 2020")
# 49 or less
print(paste0("29 or less: ", round(ecdf(weekly_tweets_2020$n)(29), 2)))

# 50 to 59
print(paste0("30 to 39: ", round(ecdf(weekly_tweets_2020$n)(39) - ecdf(weekly_tweets_2020$n)(30), 2)))

# 60 to 69
print(paste0("40 to 49: ", round(ecdf(weekly_tweets_2020$n)(49) - ecdf(weekly_tweets_2020$n)(40), 2)))

# 70 to 79
print(paste0("50 to 59: ", round(ecdf(weekly_tweets_2020$n)(59) - ecdf(weekly_tweets_2020$n)(50), 2)))

# 70 to 79
print(paste0("60 to 69: ", round(ecdf(weekly_tweets_2020$n)(69) - ecdf(weekly_tweets_2020$n)(60), 2)))

# 80 or more
print(paste0("70 or more: ", round(1 - ecdf(weekly_tweets_2020$n)(70), 2)))
print("-----------------")

# current prices
print("CURRENT PRICES (feb 2, 12:21 am)")
print("29 or less: $0.19")
print("30 to 39: $0.24")
print("40 to 49: $0.18")
print("50 to 59: $0.14")
print("60 to 69: $0.11")
print("80 or more: $0.14")

```

get probability of falling in various ranges (specific range in 2020-2021)

```{r}
weekly_tweets_2020s <- weekly_tweets[weekly_tweets$year==2021 | (weekly_tweets$year==2020 & weekly_tweets$week >= 41),]

# historical averages
print("HISTORICAL AVERAGES, tail of 2020-2021")
# 49 or less
print(paste0("29 or less: ", round(ecdf(weekly_tweets_2020s$n)(29), 2)))

# 50 to 59
print(paste0("30 to 39: ", round(ecdf(weekly_tweets_2020s$n)(39) - ecdf(weekly_tweets_2020s$n)(30), 2)))

# 60 to 69
print(paste0("40 to 49: ", round(ecdf(weekly_tweets_2020s$n)(49) - ecdf(weekly_tweets_2020s$n)(40), 2)))

# 70 to 79
print(paste0("50 to 59: ", round(ecdf(weekly_tweets_2020s$n)(59) - ecdf(weekly_tweets_2020s$n)(50), 2)))

# 70 to 79
print(paste0("60 to 69: ", round(ecdf(weekly_tweets_2020s$n)(69) - ecdf(weekly_tweets_2020s$n)(60), 2)))

# 80 or more
print(paste0("70 or more: ", round(1 - ecdf(weekly_tweets_2020s$n)(70), 2)))
print("-----------------")

# current prices
print("CURRENT PRICES (feb 2, 12:21 am)")
print("29 or less: $0.19")
print("30 to 39: $0.24")
print("40 to 49: $0.18")
print("50 to 59: $0.14")
print("60 to 69: $0.11")
print("80 or more: $0.14")

```
get probability of falling in various ranges (specific range in 2019-2021)

```{r}
weekly_tweets_2020s2 <- weekly_tweets[weekly_tweets$year==2021 | (weekly_tweets$year==2020 & weekly_tweets$week >= 41) | 
                                       (weekly_tweets$year==2019 & weekly_tweets$week >= 41),]

# historical averages
print("HISTORICAL AVERAGES, tails of 2019, 2020 and start of 2021")
# 49 or less
print(paste0("29 or less: ", round(ecdf(weekly_tweets_2020s2$n)(29), 2)))

# 50 to 59
print(paste0("30 to 39: ", round(ecdf(weekly_tweets_2020s2$n)(39) - ecdf(weekly_tweets_2020s2$n)(30), 2)))

# 60 to 69
print(paste0("40 to 49: ", round(ecdf(weekly_tweets_2020s2$n)(49) - ecdf(weekly_tweets_2020s2$n)(40), 2)))

# 70 to 79
print(paste0("50 to 59: ", round(ecdf(weekly_tweets_2020s2$n)(59) - ecdf(weekly_tweets_2020s2$n)(50), 2)))

# 70 to 79
print(paste0("60 to 69: ", round(ecdf(weekly_tweets_2020s2$n)(69) - ecdf(weekly_tweets_2020s2$n)(60), 2)))

# 80 or more
print(paste0("70 or more: ", round(1 - ecdf(weekly_tweets_2020s2$n)(70), 2)))
print("-----------------")

# current prices
print("CURRENT PRICES (feb 2, 12:21 am)")
print("29 or less: $0.19")
print("30 to 39: $0.24")
print("40 to 49: $0.18")
print("50 to 59: $0.14")
print("60 to 69: $0.11")
print("80 or more: $0.14")

```

inspect ecdf

```{r}
ecdf(weekly_tweets$n)
```


# Weekly Tweets, Graph (basic)

```{r, fig.height=6, fig.width=12}
weekly_tweets %>% 
  ggplot(aes(x = week,
             y = n,
             color = as.factor(year))) +
  geom_point(size = 2) +
  geom_line(size = 1.25,
            alpha = 0.5) +
  theme_bw() +
  labs(title = "Tweets per Week (@MCuban)",
       x = "Week of the Year",
       y = "Number of Tweets",
       color = "Year") +
  scale_x_continuous(breaks = seq(0, 52, 1)) +
  scale_y_continuous(breaks = seq(0, 160, 5)) +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank())

```

# Weekly Tweets, Graph (facet by year)

```{r, fig.height=10, fig.width=15}
weekly_tweets %>% 
  ggplot(aes(x = week,
             y = n,
             color = as.factor(year))) +
  geom_point(size = 2) +
  geom_line(size = 1.25,
            alpha = 0.5) +
  theme_bw() +
  labs(title = "Tweets per Week (@MCuban)",
       x = "Week of the Year",
       y = "Number of Tweets",
       color = "Year") +
  scale_x_continuous(breaks = seq(0, 52, 1)) +
  scale_y_continuous(breaks = seq(0, 160, 25)) +
  facet_grid(year~.)+
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank())

```

# Explore: Topics of high tweet weeks

```{r}
tweets %>% 
  filter(week == 43,
         year == 2020)
```

```{r}
tweets %>% 
  filter(week == 45,
         year == 2019)
```

# Weekly Tweets, Graph (percentile overlay)


```{r, fig.height=6, fig.width=12}

weekly_tweets %>% 
  ggplot(aes(x = week,
             y = n,
             color = as.factor(year))) +
  geom_point(size = 2) +
  geom_line(size = 1.25,
            alpha = 0.5) +
  theme_bw() +
  labs(title = "Tweets per Week (@MCuban)",
       x = "Week of the Year",
       y = "Number of Tweets",
       color = "Year") +
  scale_x_continuous(breaks = seq(0, 52, 1)) +
  scale_y_continuous(breaks = seq(0, 160, 5)) +
  geom_hline(yintercept = quantile(weekly_tweets$n, probs = c(0.01, 0.10, 0.25, 0.50, 0.75, 0.90, 0.99)),
             linetype = c("dotted", "dotted", "dotted", "solid", "dotted", "dotted", "dotted")) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.01) + 3, x = 8, label = "1st percentile", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.10) + 3, x = 8, label = "10th percentile", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.25) + 3, x = 8, label = "25th percentile", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.50) + 3, x = 8, label = "50th percentile (median)", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.75) + 3, x = 8, label = "75th percentile", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.90) + 3, x = 8, label = "90th percentile", size = 3.5) +
  annotate("text", y = quantile(weekly_tweets$n, probs = 0.99) + 3, x = 8, label = "99th percentile", size = 3.5) +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())


```

# histogram (basic)

```{r, fig.height=6, fig.width=12}
weekly_tweets %>% 
  ggplot(aes(x = n)) +
  geom_density() +
  scale_x_continuous(breaks = seq(0, 160, 5)) +
  scale_y_continuous(breaks = seq(0, 1, 0.01)) +
  labs(title = "Distribution of Tweeks per Week (@elonmusk)",
       x = "Weekly Tweet Count",
       y = "Proportion of Observations") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

```

# histogram (percentile overlay)

```{r, fig.height=6, fig.width=12}
weekly_tweets %>% 
  ggplot(aes(x = n)) +
  geom_density(size = 2) +
  scale_x_continuous(breaks = seq(0, 160, 5)) +
  scale_y_continuous(breaks = seq(0, 1, 0.001)) +
  labs(title = "Distribution of Tweeks per Week (@elonmusk)",
       x = "Weekly Tweet Count",
       y = "Proportion of Observations") +
  geom_vline(xintercept = quantile(weekly_tweets$n, probs = c(0.01, 0.10, 0.25, 0.50, 0.75, 0.90, 0.99)),
             linetype = c("dotted", "dotted", "dotted", "solid", "dotted", "dotted", "dotted")) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.01) + 1, y = 0.004, label = "1st percentile", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.10) + 1, y = 0.004, label = "10th percentile)", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.25) + 1, y = 0.004, label = "25th percentile", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.50) + 1, y = 0.004, label = "50th percentile (median)", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.75) + 1, y = 0.004, label = "75th percentile", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.90) + 1, y = 0.004, label = "90th percentile", size = 3.5, angle = 90) +
  annotate("text", x = quantile(weekly_tweets$n, probs = 0.99) + 1, y = 0.004, label = "99th percentile", size = 3.5, angle = 90) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

```

# tweets throughout a given week

```{r}
weekly_moving <-
tweets %>% 
  group_by(year, week, day) %>% 
  count(year, week, day) %>% 
  arrange(year, week, day) %>% 
  pivot_wider(names_from = day, values_from = n) %>%
  mutate_at(vars(Mon , Tue , Wed , Thu , Fri , Sat , Sun), ~replace_na(., 0)) %>% 
  mutate(sum_mon = sum(Mon, na.rm = TRUE),
         sum_tues = sum(Mon, Tue, na.rm = TRUE),
         sum_wed = sum(Mon, Tue, Wed, na.rm = TRUE),
         sum_thur = sum(Mon, Tue, Wed , Thu, na.rm = TRUE),
         sum_fri = sum(Mon, Tue, Wed , Thu , Fri, na.rm = TRUE),
         sum_sat = sum(Mon, Tue, Wed , Thu , Fri , Sat, na.rm = TRUE),
         sum_sun = sum(Mon , Tue , Wed , Thu , Fri , Sat , Sun, na.rm = TRUE))

weekly_moving


```


# graph, moving number of tweets throughout the week

```{r, fig.height=6, fig.width=12}
weekly_moving %>% 
  select(year, week, contains("sum_")) %>% 
  pivot_longer(cols = c(sum_mon, sum_tues, sum_wed, sum_thur, sum_fri, sum_sat, sum_sun),
               names_to = "day",
               values_to = "running_total") %>% 
  mutate(week = as.factor(week),
         day = factor(day, levels = c("sum_mon", "sum_tues", "sum_wed", "sum_thur", "sum_fri", "sum_sat", "sum_sun"))) %>% 
  ungroup() %>% 
ggplot(aes(x = day,
           y = running_total,
           color = week,
           group = week)) +
  geom_point() +
  geom_line() +
  scale_y_continuous(breaks = seq(0, 160, 5)) +
  theme_bw()
  
```

# quantiles, moving

```{r}
print("---mon--")
quantile(x = weekly_moving$sum_mon, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---tue--")
quantile(x = weekly_moving$sum_tues, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---wed--")
quantile(x = weekly_moving$sum_wed, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---thu--")
quantile(x = weekly_moving$sum_thur, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---fri--")
quantile(x = weekly_moving$sum_fri, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---sat--")
quantile(x = weekly_moving$sum_sat, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---sun--")
quantile(x = weekly_moving$sum_sun, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))

```
# tweets, tweets each day (not cumulative)

```{r, fig.height=6, fig.width=12}
weekly_moving %>% 
  select(year, week, Mon , Tue , Wed , Thu , Fri , Sat , Sun) %>% 
  pivot_longer(cols = c(Mon , Tue , Wed , Thu , Fri , Sat , Sun),
               names_to = "day",
               
               values_to = "daily_total") %>% 
  mutate(week = as.factor(week),
         day = factor(day, levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"))) %>% 
  ungroup() %>% 
ggplot(aes(x = day,
           y = daily_total,
           color = week)) +
  geom_jitter(width = 0.1,
              alpha = 0.5) +
  scale_y_continuous(breaks = seq(0, 160, 5)) +
  theme_bw()
  
```

histogram, with # of tweets each day

# quantiles, day total (non cumulative)

```{r}
print("---mon--")
quantile(x = weekly_moving$Mon, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---tue--")
quantile(x = weekly_moving$Tue, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---wed--")
quantile(x = weekly_moving$Wed, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---thu--")
quantile(x = weekly_moving$Thu, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---fri--")
quantile(x = weekly_moving$Fri, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---sat--")
quantile(x = weekly_moving$Sat, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))
print("---sun--")
quantile(x = weekly_moving$Sun, probs = c(0, 0.01, 0.05, seq(0.1, 0.9, 0.1), 0.95, 0.99, 1))

```




# MISC/END


